---
title: "Linear Regression Single"
output: html_document
---
Nama: Ayat Tulloh Rahulloh Khomeini
NRP: 5026211156


The Data
```{r}
download.file("http://www.openintro.org/stat/data/mlb11.RData", destfile =
"mlb11.RData")
load("mlb11.RData")
```
----------------------------------------------------------------------------------------------------------------------------------------------------------------

ON YOUR OWN
```{r}
library(ggplot2)
#first step, looks and compare each variable
pairs(mlb11)
```
```{r}
x3<-mlb11$bat_avg
y3<-mlb11$runs
plot(y3~x3)
models<-lm(y3~x3)
abline(models)
```
```{r}
cor(y3,x3)
```
1.  y^ = -642 + 5242.2 * 0.8099859
y^ = 3604.10808498
linear and relatively strong
```{r}
summary(model)
```
```{r}
summary(models)
```
2. the R^2 at_bats is 0.3729 then avg_bats is 0.6561. by the R^2 value, model avg_bats more greater than model at_bats, so it is clear that the variable bat_avg predicts runs better than at bats
```{r}
x3<-mlb11$bat_avg
y3<-mlb11$runs
plot(y3~x3)
models<-lm(y3~x3)
abline(models)
```
```{r}
hist(models$residuals)
```
```{r}
qqnorm(models$residuals)
qqline(models$residuals)
```
```{r}
cor(y3,x3)
```
```{r}
summary(models)
```
3. It had a correlation coefficient of 0.8099859 which is a strong positive correlation. Also the R^2 value is 0.6561 which is also high

```{r}
cor(mlb11$runs, mlb11$new_onbase)
cor(mlb11$runs, mlb11$new_slug)
cor(mlb11$runs, mlb11$new_obs)

summary(lm(runs ~ new_onbase, data = mlb11))
summary(lm(runs ~ new_slug, data = mlb11))
summary(lm(runs ~ new_obs, data = mlb11))
```
```{r}
x3<-mlb11$bat_avg
y3<-mlb11$runs
plot(y3~x3)
models<-lm(y3~x3)
abline(models)
```
4. After examining the summary statistics and correlation coefficients of all three new predictors new_onbase, new_slug and new_obs, the relationship between runs and new_obs variable has the highest R2 and coefficient correlation values and appears to be the best and most effective predictor of the runs.
```{r}
model5<-lm(mlb11$runs ~ mlb11$new_onbase)
plot(model5$residuals ~ mlb11$bat_avg)
abline(h=0, lty=3)
```
```{r}
hist(model5$residuals)
qqnorm(model5$residuals)
qqline(model5$residuals)
```
5. 1) there is no direct pattern.
   2) the normal quantile-quantile plot of the residuals indicates a pretty straight line so we can safely say that the residuals are approximately normaly distributed and the model meets the nearly normal residuals condition
   3) the variability of points around the least squares line still constant = variability has been met
