---
title: "R Notebook"
output: html_document
---
Nama: Ayat Tulloh Rahulloh Khomeini
NRP: 5026211156
```{r}
library(dplyr)
ads<-read.csv('C:/Users/atrke/Downloads/Advertising (1).csv')
#head(ads)
#dim(ads)
#summary(ads)
ads
```
DESCRIPTIVE
Ans_1: Not at all, ads$Sales//TV are the only have a one direction
Ans_2: The TV ads is more powerful to affected in sales, as in visualized in scatter that explain TV ads has up-trend with less outlier
```{r}
library(ggplot2)
plot(ads$Sales,ads$TV,type='p',col="red")
plot(ads$Sales,ads$Radio,type='p',col="blue")
plot(ads$Sales,ads$Newspaper, type='p',col="green")
pairs(ads)
```
DIAGNOSTIC
Ans_1:Lowest is 'Newspaper' with value of correlation 0.228299, Highest is 'TV' with value of correlation 0.782224
Ans_2: intercept is 7.0325935491277, slope is 0.0475366404330198
```{r}
library(corrplot)
num.cols<-sapply(ads, is.numeric)
cor.data<-cor(ads[,num.cols])
cor.data
corrplot(cor.data,method='color')

model_simple<-lm(Sales~TV,data=ads)
summary(model_simple)

library(broom)
tidy(model_simple)
model_multiple <- lm(Sales ~ TV + Newspaper + Radio,data=ads)
summary(model_multiple)


library(caTools)
set.seed(101)
sample<-sample.split(ads$TV,SplitRatio=0.70)
train=subset(ads,sample==TRUE)
test=subset(ads,sample==FALSE)
model<-lm(Sales~.,train)
summary(model)

res<-residuals(model)
res<-as.data.frame(res)
head(res)
```
PREDICTIVE
Ans_1: the predicted sales value for the first data point (11) is 7.058704. Similarly, the predicted sales value for the last data point (198) is 13.068875. In the meaning of words, the pred said the sales will growth around +6.010171
Ans_2:0.8972106
```{r}
sales.predictions<-predict(model,test)
sales.predictions

result<-cbind(sales.predictions,test$Sales)
result
colnames(result)<-c('pred','real')
result<-as.data.frame(result)
result

rsq=summary(model_multiple)$r.sq
rsq

```
